---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `r devtools::as.package(".")$package`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/Bisaloo/coauthors/workflows/R-CMD-check/badge.svg)](https://github.com/Bisaloo/coauthors/actions)
<!-- badges: end -->

## Installation

You can the latest version of this package from GitHub with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("bisaloo/coauthors")
```

## Usage

```{r example}
library(coauthors)
```

You can get the list of co-authors for a given person (e.g., Hugo Gruson here)
by running:

```{r, eval = FALSE}
get_coauthors("Hugo Gruson")
```

Alternatively, you can use an ORCiD. This is useful is the person of interest
has a lot of homonyms but it might result in the omission of some co-authors if
the ORCiD is absent from some publications:

```{r, eval = FALSE}
get_coauthors(orcid = "0000-0002-4094-1476")
```
